\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Global Project Manager / GPM \hfill JAN 2019 --- JUN 2020}}
\newline
\subtext{AT&T \hfill Mexico, Mexico City}
\begin{zitemize}
\item Small - medium size project coordinator.
\item Responsible for the planning, delivery and execution of external customer-facing projects.
\item AT&T’s representative acting as the customer’s single point of contact who orchestrates the analysis and solutions of telecommunications problems.
\item Responsible for the relationship with AT&T’s customers during the project management life cycle while providing expertise and analytical advise through the use of a structured project management methodology to define and carry out business objectives.
\newline
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Service Delivery Management / SDM \hfill JUN 2020 --- JUN 2021}}
\newline
\subtext{AT&T \hfill Mexico City - US}
\begin{zitemize}
\item In charge of learning and mastering the usage of internal systems as well as processes to provide the best customer experience possible.
\item Participated in drafting service budgeting, advising on areas of possible improvement to reduce costs and service delivery times.
\item Coordinated among multiple external stakeholders to gain consensus on major project milestones and prioritization goals.
\item Coordinated and led internal and external site team meetings with the goal of planning and completing future actions needed from both sides.
\end{zitemize}
\newline
%====================
% EXPERIENCE C
%====================
% \subsection{{ROLE / PROJECT C \hfill MMM YYYY --- MMM YYYY}}
% \subtext{company C \hfill somewhere, state}
% \begin{zitemize}
% \item Donec volutpat turpis et placerat pharetra.
% \item Sed sit amet sem facilisis, scelerisque lectus aliquam, accumsan purus.
% \item Aliquam at urna congue dolor luctus sodales.
% \item Quisque vitae tortor at elit tincidunt molestie sed ac quam.
% \end{zitemize}


%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}